% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{multirow}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

Quantum-Resistant Cryptography and Its Implications for Blockchain and
Cryptocurrency: A Comprehensive Mathematical Analysis

\begin{quote}
Tehzeeb Ali Gows Basha\\
Independent Researcher
\end{quote}

November 2025

\textbf{Abstract}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{1}\\
\textbf{1.1}\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
Modern public key cryptosystems rely on two assumptions regarding
computational difficulty: the integer factorization problem (RSA) and
the discrete logarithm prob-lem (elliptic curve cryptography). These
problems have stood the test of time for four decades of cryptanalysis.
Yet, their algebraic and periodic nature makes them vulnerable to
quantum algorithms, most notably Shor's algorithm (1994). This paper
presents a detailed comparison between classical and quantum-resistant
cryptographic systems with an emphasis on lattice-based systems. The
Learning With Errors (LWE) problem and its variants (Ring-LWE,
Module-LWE) do not have the same periodicity that makes problems like
integer factorization and discrete logarithms susceptible to quantum
algorithms. Furthermore, LWE problems have reductions from worst-case
lattice problems and have mathematical proofs of quantum resistance. Due
to the vulnerability of ECDSA algorithms for cryptocurrencies, it is
estimated that current cryptocurrencies will no longer be secure once
quantum computer technology matures within the next 10-30 years,
potentially compromising the value of cryptocurrencies worth over \$100
billion. The implications of cryptanalysis on public key cryptography
systems motivate mathematical recommendations regarding the security of
current cryptosystems and the need for a shift to post-quantum
cryptographic standards.

\textbf{Keywords:} Post-Quantum Cryptography, Lattice-Based
Cryptography, Modular Arithmetic, Elliptic Curves, Discrete Logarithms,
Learning With Errors, Blockchain Security

\textbf{Introduction}

\textbf{Mathematical Foundations of Classical Cryptography}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

Modern cryptography developed out of three major discoveries in
mathematics. The discov-ery of methods of testing and creating large
prime numbers was made in the 1970s. Upon the discovery of large primes,
Diffie and Hellman published a paper in 1976 describing a method of
securely exchanging keys between two parties over a public network
(Diffie \& Hellman,

1

1976). Finally, in 1977, Rivest, Shamir, and Adleman developed a system
that used the properties of large prime numbers to allow for the
encryption and secure transmission of data between two parties (Rivest
et al., 1977). Each of these systems depend upon a type of mathematical
problem that is considered to be difficult to solve, but easy to perform
by those who are supposed to be able to solve such problems.

RSA encryption, for instance, is based upon the fact that it is
difficult to factor large semiprimes (semiprimes are numbers that are
the products of two primes). Elliptic curve cryptography is based upon
the idea that it is difficult to solve the discrete logarithm problem on
elliptic curves. Both of these types of cryptographic systems perform
their operations within finite fields. RSA functions within the field of
integers modulo \emph{n}, represented as

Z\emph{∗n}. Elliptic curve cryptography functions within finite fields
of points that lie on an elliptic curve.

\textbf{1.2} \textbf{The Quantum Threat}

Within the development of quantum computing, it has become evident that
many of the cryptographic protocols used today may soon be exposed to an
existential threat if the cryp-tographic protocols are not soon modified
to account for the power of quantum computers. The algorithm known as
Shor's algorithm, for instance, can be used to solve the discrete
logarithm problem in polynomial time on a quantum computer (Shor, 1997).
Thus, any cryptographic system whose security is based upon the idea of
the intractability of the dis-crete logarithm problem (such as RSA
encryption and elliptic curve cryptography) may be broken by a
sufficiently advanced quantum computer employing Shor's algorithm.

\textbf{1.3} \textbf{Research Objectives and Scope}

The goal of this research project is to provide a thorough comparison
between classical and quantum-resistant cryptographic systems through
the performance of mathematical deriva-tions and analyses of each
system. As a result of these analyses, it will be evident to the readers
of this report that some of these classical cryptographic systems are
secure within the quantum world, but others are not. Furthermore,
blockchain technology will be covered within this report as well, which
will enable the readers of this report to become aware of the types of
cryptographic systems based upon mathematical proofs that should be
utilized in the future. Thus, the audience for this report consists of
those who wish to gain a thor-ough understanding of the mathematical
foundations of both classical and quantum-resistant cryptographic
systems.

\textbf{2 Classical Cryptographic Mathematics}

\textbf{2.1} \textbf{Modular Arithmetic}

The majority of cryptographic systems are based upon operations that
occur within mod-ular arithmetic within finite algebraic structures.
More specifically, the operations of cryp-tographic systems are often
defined within mathematical groups. For integers \emph{a, b, n}, with

2

\emph{n \textgreater{}} 0, \emph{a} is congruent to \emph{b} modulo
\emph{n}, written \emph{a ≡b} (mod \emph{n}) if \emph{n} divides the
difference between \emph{a} and \emph{b} (i.e., if \emph{n} divides the
quantity \emph{a −b}).

that are relatively prime to \emph{n}: The multiplicative group modulo
\emph{n} consists of all integers \emph{a} within the range of 1 to
\emph{n−}1

Z\emph{∗n}= \emph{\{a ∈}Z\emph{n}: gcd(\emph{a, n}) = 1\emph{\}}

This is a group that defines an operation as the multiplication of each
element of the group taken modulo \emph{n}.

\textbf{2.2} \textbf{RSA Cryptosystem}

\textbf{2.2.1 Mathematical Foundation}

The RSA cryptosystem is based upon Euler's theorem:

\textbf{Theorem 2.1.} \emph{Let a, n be integers such that} gcd(\emph{a,
n}) = 1\emph{. Then aϕ}(\emph{n})\emph{≡}1 (mod \emph{n}) \emph{for some
totient function ϕ}(\emph{n})\emph{.}

\textbf{2.2.2 Key Generation}

To generate the keys for the RSA system, the following steps are
performed:

\begin{quote}
1. Choose two different prime numbers \emph{p} and \emph{q}.

2. Calculate the value of \emph{n} as the product of \emph{p · q}, and
calculate the totient function as (\emph{p −}1)(\emph{q −}1).

3. Choose an integer \emph{e} such that the integer is within the range
(1\emph{, ϕ}(\emph{n})) and such that gcd(\emph{e, ϕ}(\emph{n})) = 1.

4. Calculate the integer \emph{d} such that \emph{d ≡e−}1(mod
\emph{ϕ}(\emph{n})).
\end{quote}

The public key for the RSA system is the key pair consisting of \emph{n}
and \emph{e}. The private key for the RSA system is the key pair
consisting of \emph{n} and \emph{d}.

\textbf{2.2.3 Encryption and Decryption}

To encrypt data within the RSA cryptosystem, the message \emph{m} is
raised to the power of \emph{e}, with all operations performed modulo
\emph{n}:

\begin{quote}
\emph{c ≡me} (mod \emph{n})
\end{quote}

To decrypt data within the RSA cryptosystem, the ciphertext \emph{c} is
raised to the power of \emph{d}, with all operations performed modulo
\emph{n}:

\begin{quote}
\emph{m ≡cd} (mod \emph{n})
\end{quote}

To prove that RSA is correct, the definition of \emph{d} must be
utilized. Since \emph{d} is defined as a value that satisfies \emph{d
≡e−}1(mod \emph{ϕ}(\emph{n})), the value \emph{d} can be rewritten in
the form an integer \emph{k}

3

such that \emph{d} = 1 + \emph{kϕ}(\emph{n}). Thus, the operation of
raising the ciphertext to the power of \emph{d} can be rewritten as
raising the value \emph{m} to some integer exponent \emph{ed}:
\emph{med}. Additionally, if the totient function is assumed to be able
to divide the quantity \emph{d −}1, then \emph{mϕ}(\emph{n})is congruent
to 1 (mod \emph{n}). Thus, decryption returns the original message
\emph{m}. (mod \emph{n}). Thus, the operation of \emph{m ·}
(\emph{mϕ}(\emph{n}))\emph{k}can be rewritten as \emph{m ·} 1\emph{k},
which is \emph{m}

\textbf{2.3} \textbf{Elliptic Curve Cryptography}

\textbf{2.3.1 Elliptic Curve Definition}

An elliptic curve is represented by the following equation:

\emph{y}2= \emph{x}3+ \emph{ax} + \emph{b}

where \emph{a, b} are elements within a finite field F\emph{p}, with
\emph{p} being a prime number that is greater than 3. Furthermore, the
quantity 4\emph{a}3+ 27\emph{b}2must not be divisible by \emph{p}.

\textbf{2.3.2 Point Addition}

The set of points that lie along an elliptic curve, together with a
point at infinity, creates an abelian group whose operation is point
addition. For two points that are included within the elliptic curve,
the point that is created as a result of adding the two points together
includes coordinates that are defined according to the following
equations:

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule()
\multicolumn{2}{@{}>{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.6667} + 2\tabcolsep}}{%
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\emph{λ} =\emph{y}2 \emph{−y}1 (mod \emph{p})
\end{quote}

\emph{x}3 = \emph{λ}2\emph{−x}1 \emph{−x}2

\begin{quote}
\emph{y}3 = \emph{λ}(\emph{x}1 \emph{−x}3) \emph{−y}1\\
\emph{x}2 \emph{−x}1 (mod \emph{p})
\end{quote}

(mod \emph{p})\strut
\end{minipage}} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
(1)\\
(2)\\
(3)
\end{quote}\strut
\end{minipage} \\
\midrule()
\endhead
\multicolumn{3}{@{}>{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{1.0000} + 4\tabcolsep}@{}}{%
The point that is created is represented by the coordinates
(\emph{x}3\emph{, y}3). If the two points that are being added together
are identical to one another, the value of \emph{λ} is represented
as3\emph{x}2 2\emph{y}1 1+\emph{a}

(mod \emph{p}).} \\
\textbf{2.3.3} &
\multicolumn{2}{>{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.6667} + 2\tabcolsep}@{}}{%
\begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
\textbf{The Elliptic Curve Discrete Logarithm Problem}
\end{quote}
\end{minipage}} \\
\bottomrule()
\end{longtable}

In elliptic curve cryptography, one of the problems that must be solved
is the elliptic curve discrete logarithm problem (ECDLP):

\textbf{Definition 2.1.} \emph{Let P and Q be two points that are
defined within an elliptic curve. The elliptic curve discrete logarithm
problem is the problem of determining the integer k such that Q} =
\emph{kP.}

The elliptic curve discrete logarithm problem is considered to be a
difficult problem to solve within classical computing algorithms; the
best-known algorithms require on the order of\emph{√n} operations to
solve the discrete logarithm problem in elliptic curves, where \emph{n}
is the order of the elliptic curve group.

4

\textbf{2.4} \textbf{The Discrete Logarithm Problem}

In the finite field F\emph{p}, where \emph{p} is a prime number, let
\emph{G} be the multiplicative group whose elements have order \emph{n},
where \emph{n} is a divisor of \emph{p −}1. Additionally, let \emph{g}
be a generator for that group.

\textbf{Definition 2.2.} \emph{Let G be a finite cyclic group of order n
with a generator g. The discrete logarithm problem is, given an element
h within G, to determine the integer x such that gx}= \emph{h.}

Discrete logarithms problems are utilized within cryptographic systems
such as the Diffie-Hellman and ElGamal systems.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{3}\\
\textbf{3.1}\\
\textbf{3.1.1}\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Quantum Computing Fundamentals and Cryptographic Vulnerability}

\textbf{Quantum Computing Basics}

\textbf{Quantum Bits (qubits) and Superposition}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

A qubit is a unit of information that can exist in a state of
superposition. Thus, a qubit can be in a state of 0, 1, or both at the
same time. A qubit can be represented as a linear combination of its
basis states. Thus, a qubit can be represented as the linear combination
\emph{α \textbar{}}0\emph{⟩}+ \emph{β \textbar{}}1\emph{⟩}, where
\emph{α} and \emph{β} are complex numbers whose modulus is equal to one:
\emph{\textbar α\textbar{}}2+ \emph{\textbar β\textbar{}}2= 1.

\textbf{3.1.2 Quantum Gates}

Quantum gates are the operators that act upon the quantum bits within a
quantum com-puter. A few of the more common quantum gates include the
Hadamard gate, the Pauli-X gate (also known as the NOT gate), the CNOT
gate, and the SWAP gate.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}@{}}
\toprule()
\multirow{4}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\textbf{3.2}
\end{minipage}} &
\multicolumn{2}{>{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2857} + 2\tabcolsep}}{%
\begin{minipage}[b]{\linewidth}\raggedright
Hadamard gate: \emph{H} = 1\emph{√}2
\end{minipage}} & \begin{minipage}[b]{\linewidth}\raggedright
1\\
1\strut
\end{minipage} &
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
1\\
\emph{−}1\strut
\end{minipage}} &
\multirow{5}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
0\\
0\\
0\\
1
\end{quote}\strut
\end{minipage}} &
\multirow{5}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
0 0 1 0
\end{quote}
\end{minipage}} \\
& \begin{minipage}[b]{\linewidth}\raggedright
Pauli-X gate: \emph{X} =
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
0\\
1\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
1\\
0
\end{quote}\strut
\end{minipage} \\
&
\multicolumn{2}{>{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2857} + 2\tabcolsep}}{%
\begin{minipage}[b]{\linewidth}\raggedright
CNOT gate: CNOT =
\end{minipage}} &
\multirow{3}{*}{\begin{minipage}[b]{\linewidth}\raggedright
1

0

0

0
\end{minipage}} &
\multirow{3}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
0\\
1\\
0\\
0
\end{quote}\strut
\end{minipage}} \\
&
\multicolumn{2}{>{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2857} + 2\tabcolsep}}{%
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Shor's Algorithm}
\end{quote}
\end{minipage}} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{3.2.1}
\end{minipage} &
\multicolumn{2}{>{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2857} + 2\tabcolsep}}{%
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Overview}
\end{quote}
\end{minipage}} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

The most common algorithm for factoring integers (known as Shor's
algorithm) can factor any integer in time \emph{O}((log \emph{N})3).
Thus, the algorithm is based upon the use of quantum

5

Fourier transforms to perform the factorization. The algorithm is
performed according to the following steps:

\begin{quote}
1. Choose a random integer \emph{a} within the range of integers between
1 and \emph{N −}1 (inclusive) such that gcd(\emph{a, N}) = 1.

2. Determine the period \emph{r} of the function \emph{f}(\emph{x}) =
\emph{ax}(mod \emph{N}) with the use of quantum Fourier transforms.

3. If the calculated value for \emph{r} is even, and if the value of
\emph{ar/}2is not congruent to -1 (mod \emph{N}), calculate the integers
gcd(\emph{ar/}2+ 1\emph{, N}) and gcd(\emph{ar/}2\emph{−}1\emph{, N}).
Each of these integers will be a factor of the original number \emph{N}.
\end{quote}

\textbf{3.2.2 Mathematical Foundation}

The algorithm relies upon the fact that factoring integers can be
reduced to the problem of determining the period of a function. Thus,
within the quantum computer, quantum Fourier transforms are utilized to
determine that period. For integer \emph{N}, choose a value for \emph{Q}
as 2\emph{q} where the value of \emph{N}2is less than or equal to
\emph{Q} and is less than 2\emph{N}2.

\begin{quote}
The initial state of the quantum computer is the state:
\end{quote}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule()
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\emph{\textbar ψ⟩}=
\end{minipage}} &
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
1\\
\emph{\sout{√}Q}\strut
\end{minipage}} & \begin{minipage}[b]{\linewidth}\raggedright
\emph{Q−}1
\end{minipage} &
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\emph{\textbar x⟩\textbar{}}0\emph{⟩}
\end{quote}
\end{minipage}} \\
& & \begin{minipage}[b]{\linewidth}\raggedright
\emph{x}=0
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

Apply the function \emph{f}(\emph{x}) = \emph{ax}(mod \emph{N}) to both
registers of the quantum computer. Thus, the new state of the quantum
computer is:

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
\toprule()
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\emph{\textbar ψ⟩}=
\end{minipage}} &
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
1\\
\emph{√Q}\strut
\end{minipage}} & \begin{minipage}[b]{\linewidth}\raggedright
\emph{Q−}1
\end{minipage} &
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\emph{\textbar x⟩\textbar ax}
\end{quote}
\end{minipage}} &
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
(mod \emph{N})\emph{⟩}
\end{quote}
\end{minipage}} \\
& & \begin{minipage}[b]{\linewidth}\raggedright
\emph{x}=0
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

Measure the second register of the quantum computer. The state of the
first register will collapse to a state that represents the period
\emph{r}. Apply a quantum Fourier transform to the first register.
Measure the first register again. The value of the measurement will be
the value of the period \emph{r}.

\textbf{3.2.3 Complexity}

The complexity of classical integer factoring algorithms is generally of
the order exp((log \emph{n})1\emph{/}3(log log \emph{n})2\emph{/}3). The
complexity of Shor's quantum factoring algorithm is \emph{O}((log
\emph{n})3).

\textbf{3.3} \textbf{Elliptic Curve Cryptography}

In addition to the factoring problem, Shor's algorithm can also be used
to solve the discrete logarithm problem on elliptic curves. Thus, the
elliptic curve cryptosystems that rely upon the difficulty of solving
such a discrete logarithm problem can also be broken by a quantum
computer that utilizes Shor's algorithm to solve the problem (Shor,
1997). Thus, the elliptic curve discrete logarithm problem can be solved
in time \emph{O}((log \emph{n})3), where \emph{n} is the order of the
elliptic curve group.

6

\textbf{4 Quantum-Resistant Cryptographic Mathematics}

\textbf{4.1} \textbf{Lattice Theory Foundations}

\textbf{Definition 4.1} (Lattice)\textbf{.} \emph{A lattice within}
R\emph{nis a discrete subgroup that is generated by a set of n linearly
independent vectors within the same space.}

\emph{n} linearly independent basis vectors within that lattice. Thus,
the lattice consisting of all Thus, a lattice \emph{L} can be
represented as a set of all of the linear combinations of the

linear combinations of \emph{n} linearly independent basis vectors
\emph{b}1\emph{, b}2\emph{, ..., bn} is represented as:

\begin{quote}
\emph{n}\\
\emph{L} = \emph{\{ i}=1 \emph{zibi \textbar{} zi ∈}Z\emph{\}}
\end{quote}

The matrix that is constructed from the linear combination of the basis
vectors within the lattice is referred to as the basis matrix of that
lattice.

\textbf{4.1.1 Fundamental Lattice Problems}

\textbf{Definition 4.2} (Shortest Vector Problem (SVP))\textbf{.}
\emph{Given a lattice within} R\emph{n, find the non-zero vector within
that lattice whose length is the shortest.}

\textbf{Definition 4.3} (Closest Vector Problem (CVP))\textbf{.}
\emph{Given a lattice within} R\emph{n, and a target vector in that same
space, find the vector within the lattice whose distance to the target
vector is the shortest.}

The Shortest Vector Problem (SVP) has been proven to be an NP-hard
problem in classical computation {[}1{]}. Furthermore, no known
algorithm for solving the SVP has been proven to be solvable in
polynomial time by a quantum computer.

\textbf{4.2} \textbf{Learning With Errors (LWE) Problem}

\textbf{4.2.1 Problem Definition}

\textbf{Definition 4.4.} \emph{Let n, q be positive integers, and let χ
be some distribution of values over the integers modulo q. Furthermore,
let s be a vector that is secret to the sender and receiver of some
information. The Learning With Errors (LWE) problem is the problem of
generating a distribution of pairs} (\emph{a, b}) \emph{where a is a
vector of n dimensions whose entries are elements of} Z\emph{q, and
where b is the inner product of a and s (the sum of the products of each
component of a and s) plus some error e whose distribution is
represented by the distribution χ. Fur-thermore, the Search-LWE problem
is the problem of finding s given enough samples of the distribution of
pairs} (\emph{a, b})\emph{. Finally, the Decision-LWE problem is the
problem of recognizing samples of the distribution of pairs} (\emph{a,
b}) \emph{generated using the Search-LWE distribution from
randomly-sampled pairs} (\emph{a, b}) \emph{from the distribution}
Z\emph{n q×} Z\emph{q.}

7

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{4.2.2}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Error Distribution}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\multicolumn{2}{@{}>{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{1.0000} + 2\tabcolsep}@{}}{%
\begin{minipage}[t]{\linewidth}\raggedright
One of the most common choices of distribution for the error \emph{e} in
the LWE problem is the discrete Gaussian distribution
\emph{D}Z\emph{,σ}. The discrete Gaussian distribution has a probability
distribution function of:

\begin{quote}
\emph{D}Z\emph{,σ}(\emph{x}) = exp(\emph{−πx}2\emph{/σ}2)\\
\emph{z∈}Zexp(\emph{−πz}2\emph{/σ}2)
\end{quote}\strut
\end{minipage}} \\
\textbf{4.3} & \begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
\textbf{Security Reduction: LWE to Lattice Problems}
\end{quote}
\end{minipage} \\
\multicolumn{2}{@{}>{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{1.0000} + 2\tabcolsep}@{}}{%
\textbf{Theorem 4.1.} \emph{Let n, q be positive integers such that q is
a prime number and q is greater than or equal to} 2\emph{√n.
Furthermore, let α be some positive decimal that is less than 1 such
that αq is greater than or equal to} 2\emph{√n. Then, if there is an
algorithm that can solve the}

\emph{Decision-LWE problem with non-negligible probability relative to
the size of its inputs, there}

\emph{is an algorithm that can solve worst-case instances of the lattice
problems GapSV P} ˜\emph{O}(\emph{n/α})\emph{and}

\emph{SIV P} ˜\emph{O}(\emph{n/α})\emph{{[}8{]}.}} \\
\textbf{4.4} & \begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
\textbf{Ring-LWE}
\end{quote}
\end{minipage} \\
\bottomrule()
\end{longtable}

Ring-LWE (Learning With Errors over Rings) was developed as a means of
improving the efficiency of the LWE problem. Thus, Ring-LWE shares many
of the same features as the LWE problem (both in form and function), but
has a structure that permits for it to be implemented more efficiently
than the original LWE problem.

\textbf{Definition 4.5} (Ring-LWE)\textbf{.} \emph{Let R be the set of
polynomials of degree less than n with integer coefficients, denoted as}
Z{[}\emph{x}{]}\emph{/}(\emph{xn}+ 1)\emph{. Furthermore, let Rq be the
set of polynomials in R whose coefficients are elements of} Z\emph{q:
Rq} = \emph{R/q}Z{[}\emph{x}{]}\emph{. Ring-LWE is defined in the same
way as the LWE problem, but within this ring Rq: samples of the form}
(\emph{a, b}) \emph{where a is within Rq, b is the inner product of a
and some secret vector s within the ring Rq, and some error distributed
according to the error distribution over the ring R.}

Ring-LWE has been proven to offer significant improvements to the
efficiency of the algorithm relative to LWE while maintaining the same
security guarantees of LWE.

\textbf{4.5} \textbf{Module-LWE}

Module-LWE is a generalization of both the LWE and the Ring-LWE
algorithms.

\textbf{Definition 4.6} (Module-LWE)\textbf{.} \emph{Let Rq be the set
of polynomials of degree less than n with coefficients in} Z\emph{q: Rq}
= Z\emph{q}{[}\emph{x}{]}\emph{/}(\emph{xn}+ 1)\emph{. Furthermore, let
d be any positive integer that is greater than 1. Then Module-LWE can be
defined as a distribution of samples of the form} (\emph{a, b})
\emph{wherein a is within Rd q, the set of d-dimensional vectors whose
entries are elements of Rd q, s is a secret vector within Rd q, and the
error between the inner product of a and s is distributed according to
the error distribution over the ring R.}

Module-LWE provides a generalization of both the LWE and Ring-LWE
algorithms that permits for a balance to be struck between security and
efficiency of the algorithms.

8

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{5}\\
\textbf{5.1}\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Mathematical Comparison: Classical vs. Quantum-Resistant}

\textbf{Algebraic Structure Analysis}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

Table 1 presents a comparison of the classical and quantum-resistant
cryptographic systems. The classical systems, such as RSA and ECDSA,
rely upon the structure of cyclic groups and the difficulty of the
discrete logarithm problem within those groups. The quantum-resistant
systems, such as the lattice-based algorithms, utilize
\emph{n}-dimensional lattices instead.

\textbf{5.2} \textbf{Why Quantum Algorithms Fail on Lattices}

\textbf{5.2.1 Absence of Periodicity}

Shor's algorithm finds the period of the function:

\begin{quote}
\emph{f}(\emph{x}) = \emph{ax} (mod \emph{N})
\end{quote}

where \emph{ar≡}1 (mod \emph{N}) for some value of \emph{r}. No such
period exists for problems like the Learning with Errors problem:

\begin{quote}
\emph{f}(\emph{a}) = \emph{⟨a, s⟩}+ \emph{e} (mod \emph{q})
\end{quote}

\textbf{5.2.2 Worst-Case to Average-Case Reduction}

While classical cryptographic algorithms are based upon problems that
are difficult to solve on average, lattice problems are difficult in the
worst case. However, there is a proof that if someone can find an
efficient algorithm for solving the average case of the problem, then
that same algorithm can be used to solve the worst case instance of the
same problem for any lattice.

\textbf{Theorem 5.1} (Worst-Case Hardness)\textbf{.} \emph{Suppose an
attacker can solve instances of the average-case Learning With Errors
problem with probability \textgreater{}}\uline{1 2}+\emph{ϵ for some
constant ϵ \textgreater{}} 0\emph{. Then the same algorithm can solve
instances of the worst-case GapSVP problem with approximation factor γ}
= \emph{O}(\emph{\uline{n}α})\emph{.}

\begin{quote}
The function ˜\emph{O}(\emph{·}) hides factors that are polynomial in
\emph{n}.
\end{quote}

\textbf{5.3} \textbf{Security Parameter Analysis}

The following table compares some of the different classical and
quantum-resistant crypto-graphic systems in terms of their
quantum-resistant security parameters.

9

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Property}
\end{quote}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Classical}
\end{quote}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Lattice-Based}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
Quantum Resistance Quantum Security\\
Hard Problem\\
Best Classical Attack Best Quantum Attack Key Size
\end{quote}\strut
\end{minipage} & \begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
Group Theory\\
RSA\\
Shor's Algorithm Subexponential\\
Polynomial\\
256 bits
\end{quote}\strut
\end{minipage} & \begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
Lattice Theory\\
Factoring\\
Grover's Algorithm Exponential\\
Exponential\\
1-3 KB
\end{quote}\strut
\end{minipage} \\
\bottomrule()
\end{longtable}

Table 1: Comparison of classical and quantum-resistant cryptographic
systems

\textbf{6 Post-Quantum Cryptography Standards}\\
\textbf{6.1} \textbf{NIST Standardization Process}\\
The National Institute of Standards and Technology (NIST) is creating
cryptographic stan-dards that are secure from attacks by quantum
computers. The process began in 2016 with the goal of having the
standards published by 2024 {[}6{]}.

\textbf{6.2} \textbf{Selected Algorithms}\\
\textbf{6.2.1} \textbf{CRYSTALS-Kyber (FIPS 203)}\\
CRYSTALS-Kyber (standardized by NIST as ML-KEM) is a KEM whose security
is based upon the Module-LWE problem. This system uses the following
parameters:\\
• \emph{n} = 256\\
• \emph{q} = 3329\\
• \emph{k ∈\{}2\emph{,} 3\emph{,} 4\emph{\}}\\
The process for key generation is as follows:\\
1. Sample a matrix \emph{A} of size \emph{k × k} with elements uniformly
distributed in Z\emph{q}\\
2. Sample a secret vector \emph{s} of size \emph{n} with entries sampled
from a centered binomial distribution\\
3. Sample a vector \emph{e} of size \emph{n} with entries sampled from a
centered binomial distribution 4. Calculate \emph{t} = \emph{As} +
\emph{e} (mod \emph{q}).

The public key is (\emph{A, t}) and the shared secret key is \emph{s}.

10

\textbf{6.2.2 CRYSTALS-Dilithium (FIPS 204)}

CRYSTALS-Dilithium is a digital signature system whose security is based
upon the Module-LWE problem. For each signature:

\begin{quote}
1. Sample a random value \emph{y}.

2. Calculate \emph{w} = \emph{Ay}.

3. Calculate the challenge value \emph{c} = \emph{H}(\emph{w, M}) where
\emph{H} is a cryptographic hash function and \emph{M} is the message
being signed.

4. Calculate the signature \emph{z} = \emph{y} + \emph{cs}.

5. If the sizes of \emph{z} or \emph{w −ct} are outside some pre-defined
bounds, repeat steps 1-3 until the signature is accepted.
\end{quote}

\textbf{6.2.3 FALCON (FIPS 205)}

FALCON is another digital signature system. However, unlike the others
based upon the Module-LWE problem, FALCON uses the NTRU lattice problem
and the GPV framework for digital signatures. Fast Fourier sampling is
used in its creation of the digital signatures.

\textbf{6.3} \textbf{Security Levels}

The standards provide for three security levels, each of which is
roughly equivalent to a certain level of security in classical
cryptography:

\begin{quote}
• Level 1: AES-128 (approximately 143 quantum bits)

• Level 3: AES-192 (approximately 207 quantum bits)

• Level 5: AES-256 (approximately 272 quantum bits)
\end{quote}

\textbf{7 Implications for Blockchain and Cryptocurrency}

\textbf{7.1} \textbf{Current Cryptographic Infrastructure}

\textbf{7.1.1 Bitcoin}

Bitcoin uses the ECDSA algorithm with the secp256k1 elliptic curve for
digital signatures. Given the public key (\emph{P}) and the private key
(\emph{d}), the signature for a message (\emph{m}) is created with the
following equations:

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\emph{r} = (\emph{kG})\emph{x}\\
\emph{s} = \emph{k−}1(\emph{H}(\emph{m}) + \emph{rd})
\end{quote}\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
(mod \emph{n})
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

where \emph{k} is a random value, \emph{G} is a generator for the
elliptic curve, \emph{m} is the message being signed, and \emph{n} is
the size of the elliptic curve. Should an attacker obtain the public key
for a Bitcoin address, however, they could use Shor's algorithm to
mathematically recover the private key associated with that address.

11

\textbf{7.1.2 Ethereum}

Like Bitcoin, Ethereum utilizes the elliptic curve and ECDSA to create
digital signatures for its transactions. Instead of using the public key
of an address as its address on the Ethereum blockchain, Ethereum
calculates the Keccak-256 hash of the public key to form the address of
the account.

\textbf{7.2} \textbf{Threat Timeline}

Table 2 presents the estimated year-by-year technological developments
in quantum com-puters. Beyond some threshold number of qubits in a
quantum processor, those quantum computers will be able to pose a threat
to the public key cryptography currently in use. There is no exact date
for when cryptographically relevant quantum computers will be available
to the public, but various estimates exist.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Year}
\end{quote}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Technology}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
2019--2023

2025--2030

2030--2035
\end{quote}
\end{minipage} & \begin{minipage}[t]{\linewidth}\raggedright
\begin{quote}
Google announced that it had achieved quantum supremacy with a 53-qubit
processor. IBM announced the Condor processor with 1,121 qubits.

Estimates for the emergence of cryptographically relevant quantum
computers (CRQCs).

Estimates for when such quantum computers will pose a widespread threat
to the public key cryptography currently in use.
\end{quote}
\end{minipage} \\
\bottomrule()
\end{longtable}

Table 2: Quantum computing development timeline

\textbf{7.3} \textbf{Attack Scenarios}

\textbf{7.3.1 Store-Now-Decrypt-Later (SNDL)}

In this type of attack, an attacker harvests the cryptocurrencies made
with blockchain tech-nology, stores them, and decrypts them with the
power of a quantum computer. While not currently possible for such
attacks to occur, the exposure of public keys to the blockchain presents
the potential for such an attack to occur should quantum computers
become avail-able.

\textbf{7.3.2 Direct Key Recovery}

Once an attacker gains access to a quantum computer, those public keys
stored on the blockchain can be directly attacked in order to recover
the private keys associated with those public keys. Estimates suggest
that this type of attack will take between hours and days to execute for
cryptocurrencies with 256-bit keys. Thus, those addresses associated
with public keys will be at risk of having their cryptocurrencies
compromised.

12

\textbf{7.4} \textbf{Economic Impact Assessment}

The total market for Bitcoin is currently valued at \$800 billion. The
market for Ethereum is valued at \$300 billion. The total market value
of all cryptocurrencies is \$2 trillion. The number of public keys
exposed on the blockchain represents 20-30\% of the total supply of
Bitcoin. Furthermore, another estimate suggests that 15-20\% of the
total supply of Bitcoin is represented by addresses associated with
public keys whose private keys are lost or inac-cessible (Satoshi's
coins). Thus, the total value of the cryptocurrencies that are at risk
of being decrypted by quantum computers is between \$100 billion and
\$300 billion.

\textbf{7.5} \textbf{Migration Strategies}

\textbf{7.5.1 Hard Fork}

A hard fork of the blockchain will require the creation of a new version
of the protocol. Such a protocol will require:

\begin{quote}
• New cryptographic algorithm

• New protocol version

• Implementation of a period for the migration of cryptocurrencies from
the old to the new blockchain protocol

• Freezing of the addresses of those who do not participate in the
protocol change
\end{quote}

One of the challenges to implementing such a protocol will be the
decentralized nature of the blockchain. Furthermore, many of the public
keys in use on the blockchain do not have their associated private keys.
Other challenges will be the need to create the new protocol in a way
that is backwards compatible with the existing protocol, as well as to
account for the increased sizes of transactions that will need to be
created under the new cryptographic algorithm.

\textbf{7.5.2 Hybrid Cryptography}

An alternative to creating a hard fork in the blockchain is the
implementation of a hybrid cryptographic system. Such a system will
utilize both classical and post-quantum crypto-graphic algorithms for
the creation of digital signatures. For instance, one blockchain system
can use ECDSA signatures while another uses digital signatures based
upon the Module-LWE problem.

Some of the advantages of a system like this will be that even if the
classical crypto-graphic system is broken, the transactions will still
be secure. Furthermore, the use of the same general processes for the
creation of digital signatures as are currently utilized on the
blockchain means that there will be no need to make changes to the
blockchain itself to implement such a system. Some of the disadvantages
of this system will be the doubling of the size of digital signatures,
as well as the increased length of time required to verify each digital
signature and transaction created under this system.

13

\textbf{8 Implementation Case Study}

\textbf{8.1} \textbf{Post-Quantum Bitcoin Prototype}

\textbf{8.1.1 Design Specifications}

The design of a post-quantum version of Bitcoin will utilize the
CRYSTALS-Dilithium digital signature system, which provides security at
the NIST security level 2. The public keys will be of size 1,312 bytes
(compared to 33 bytes in ECDSA), the digital signatures will be of size
2,420 bytes (compared to 71 bytes in ECDSA), and the time required for
signature verification will be around 200 microseconds (compared to 50
microseconds for ECDSA).

\textbf{8.1.2 Performance Analysis}

Currently, the size of a Bitcoin transaction is around 250 bytes.
Therefore, the size of transactions will increase to 2,600 bytes for the
post-quantum system. Furthermore, the current number of transactions
that can occur within a block is between 2,000 and 2,500. Thus, only
between 200 and 250 transactions will be able to fit within a block for
the post-quantum system.

\textbf{8.1.3 Scalability Solutions}

Some of the possible solutions to the scalability issue of Bitcoin will
be to:

\begin{quote}
• Increase the size of the block

• Implement signature aggregation algorithms

• Develop Layer-2 solutions (like the Lightning network)

• Implement optimized implementations of the post-quantum protocol
\end{quote}

\textbf{8.2} \textbf{Ethereum Post-Quantum Considerations}

\textbf{8.2.1 Smart Contract Implications}

The implications of the shift to digital signatures based upon the
Module-LWE problem will include changes to the way that smart contracts
verify digital signatures of transactions. In addition, the creation of
multi-signature wallets will change. Finally, the gas costs for smart
contracts to verify digital signatures will change. Currently, smart
contracts require around 3,000 units of gas to verify digital
signatures. In contrast, the CRYSTALS-Dilithium digital signature system
will require between 100,000 and 500,000 units of gas for signature
verification.

\textbf{8.2.2 Protocol Upgrades}

The protocol for Ethereum will have to be changed to include smart
contracts that support the new digital signatures. For instance, the
protocol can change its smart contracts to

14

create a type of transaction that uses these new types of digital
signatures. Furthermore, the protocol can change its account abstraction
system (EIP-4337) to handle these new digital signatures. Finally, the
protocol can create new precompiles to speed the verification of these
digital signatures.

\textbf{9 Discussion}

\textbf{9.1} \textbf{Mathematical Foundations}

The main goal of this research was to investigate some of the
differences between classical cryptographic systems and post-quantum
cryptographic systems. As discussed above, classi-cal cryptographic
systems mainly work within the context of cyclic groups (both finite
fields and elliptic curves) and the discrete logarithm problem that
exists within those groups. In contrast, the mathematical framework for
lattice-based cryptographic systems is based upon the
\emph{n}-dimensional Euclidean spaces within which there is no
periodicity to the algorithms.

Another of the main differences between classical cryptographic systems
and lattice-based cryptographic systems is the link between worst-case
and average-case problems for those systems. When using lattice-based
cryptographic systems, an algorithm that is efficient at solving
average-case instances will also be efficient at solving the worst-case
instance of the same problem. However, classical cryptographic systems
rely upon the assumption that problems are difficult to solve on average
but relatively easy to solve in the worst case.

Finally, the reasons that no efficient quantum algorithms have yet been
created for lattice-based cryptographic systems are these mathematical
differences between the systems. For instance, the cyclic groups within
which classical cryptographic systems are based have an inherent
periodicity to their problems, which allows quantum algorithms like
Shor's algo-rithm to efficiently find the period and solve the problem.
The lack of periodicity within lattice problems explains the inability
of current quantum algorithms to efficiently solve those problems.

\textbf{9.2} \textbf{Performance}

One of the main findings of this research is that post-quantum
cryptographic systems are significantly less performant than classical
cryptographic systems. For instance, public keys based upon
quantum-resistant cryptographic systems will be 40-50 times larger than
those created by the ECDSA algorithm for Bitcoin. Additionally, digital
signatures will be 30-40 times larger in size. Furthermore, the
computational costs of using these new systems will be 2-10 times
greater than those of classical cryptographic systems. Despite these
disadvantages, however, the cryptographic systems were still considered
to be acceptable for use due to the existential threat that quantum
computers pose to current cryptographic systems.

\textbf{9.2.1 Implementation Challenges}

Beyond the performance differences between the two types of
cryptographic systems, there are other challenges to the implementation
of these quantum-resistant cryptographic systems to cryptocurrencies
like Bitcoin and Ethereum. Some of these challenges include:

15

\begin{quote}
• Bandwidth requirements for the larger public keys and digital
signatures

• Storage requirements for the blockchain to store the larger digital
transactions

• Increased computational requirements for the blockchain nodes to
verify digital signa- tures

• Backwards compatibility with existing cryptocurrencies
\end{quote}

\textbf{9.3} \textbf{Timeline Urgency}

Given the current rate of development of quantum computers, it will take
between 10 and 30 years for those quantum computers to reach the number
of qubits that will allow them to pose a threat to current cryptographic
systems {[}6{]}. Thus, while it may appear that no action is required in
the present, such action is imperative to take. Should quantum
computers, however, develop at a faster rate than these current
estimates, the urgency to find a solution will be even greater than that
indicated by the 10-30 year estimate.

\textbf{9.4} \textbf{Future Research}

Beyond the research that has already been performed on quantum-resistant
cryptography, there are a few suggestions for future research in this
area. Some of the possible directions for future research in this field
include:

\begin{quote}
• Optimized implementations of the proposed cryptographic systems

• Development of other types of hybrid cryptographic schemes

• Development of techniques to aggregate digital signatures to reduce
the overhead of using the proposed post-quantum cryptographic algorithms

• Exploration of other types of cryptographically hard problems

• Development of quantum-resistant smart contracts
\end{quote}

\textbf{10} \textbf{Conclusion}

This research presents a detailed and comprehensive analysis of the
mathematical reasons that classical cryptographic systems fail against
quantum attacks, while also demonstrating the security of lattice
problems against such quantum attacks. The main mathematical difference
between classical and quantum-resistant systems is the structure of the
problems that are utilized in those systems. While classical
cryptography makes use of cyclic groups that inherently do have periodic
structure that is targeted by quantum algorithms, lattice problems do
not have this same structure.

Furthermore, the fact that breaking the average case of a lattice
problem is equivalent to breaking the worst case of that problem
provides a solid theoretical foundation for the security of these
cryptographic systems.

16

For cryptocurrencies like Bitcoin and Ethereum, such a threat poses both
an existing and imminent danger. As digital signatures that are based on
elliptic curves will be broken by quantum computers within 10 to 30
years, the data and cryptocurrencies of affected users will be at risk
of compromise. Thus, though at the cost of the increased sizes of keys,
digital signatures, and computational costs for those signatures, it is
necessary to implement cryptographic systems that are secure against
quantum computers.

Thus, it is imperative that each of the cryptocurrencies create plans to
implement post-quantum cryptographic systems such as Kyber, Dilithium,
and FALCON. Such plans may include the creation of hybrid cryptographic
systems to provide security for both the classical and the post-quantum
systems. Furthermore, scalability solutions will need to be created to
combat any decrease in the throughput of the blockchains. Finally, it
will also be necessary to create timelines for such an upgrade, as well
as to perform security audits on the proposed systems prior to their
implementation.

Overall, the mathematical foundations of these systems are solid, the
algorithms are standardized, and the threat timeline is clear. Thus, the
blockchain and cryptocurrency communities must take action to ensure the
long-term security of their systems against quantum computers.

\textbf{Acknowledgments}

The author acknowledges the foundational work of researchers in
post-quantum cryptog-raphy, particularly the contributions of Oded
Regev, Chris Peikert, and the NIST Post-Quantum Cryptography project
team.

\textbf{References}

\begin{quote}
{[}1{]} Ajtai, M. (1998). The shortest vector problem in \emph{L}2 is
NP-hard for randomized re-ductions. \emph{Proceedings of the 30th Annual
ACM Symposium on Theory of Computing}, 10-19.

{[}2{]} Bernstein, D. J., \& Lange, T. (2017). Post-quantum
cryptography. \emph{Nature}, 549(7671), 188-194.

{[}3{]} BTQ Technologies. (2025). BTQ Technologies announces
quantum-safe Bitcoin using NIST-standardized post-quantum cryptography.
Retrieved from

{[}4{]} Chainalysis. (2023). Quantum computing and crypto security.
Retrieved from

{[}5{]} Chen, Y. (2024). Polynomial-time quantum algorithm for the
principal ideal problem and applications to cryptanalysis.
\emph{Preprint}.

{[}6{]} Diffie, W., \& Hellman, M. (1976). New directions in
cryptography. \emph{IEEE Transactions on Information Theory}, 22(6),
644-654.
\end{quote}

17

\begin{quote}
{[}7{]} National Institute of Standards and Technology. (2024).
\emph{Federal Information Processing Standards Publication 203, 204,
205: Post-Quantum Cryptography Standards}.

{[}8{]} Peikert, C. (2014). Lattice cryptography for the internet.
\emph{IACR Cryptology ePrint Archive}.

{[}9{]} Regev, O. (2005). On lattices, learning with errors, random
linear codes, and cryp-tography. \emph{Proceedings of the 37th Annual
ACM Symposium on Theory of Computing}, 84-93.
\end{quote}

{[}10{]} Rivest, R. L., Shamir, A., \& Adleman, L. (1978). A method for
obtaining digital signa-tures and public-key cryptosystems.
\emph{Communications of the ACM}, 21(2), 120-126.

{[}11{]} Shor, P. W. (1994). Algorithms for quantum computation:
Discrete logarithms and factoring. \emph{Proceedings of 35th Annual
Symposium on Foundations of Computer Science}, 124-134.

{[}12{]} The Quantum Insider. (2024). Blockchain and quantum computing
are on a collision course. Retrieved from

{[}13{]} TII Insights. (2024). Navigating the quantum frontier: Arrival
of NIST's first post-quantum cryptography standards. Retrieved from

18

\end{document}
